Verifying Demonstrations

### 2018-02-01 paper/RelatedWork.tex
Removes beamerarticle and changes citations to natbib syntax

\mode*
\section{Related work}%
\label{RelatedWork}

\mode<presentation>{%
\subsection{Image-based methods}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{solution}[Jacob's method]
    \begin{itemize}
      \item Take aerial photos of the event.
      \item Divide area into regions.
      \item Estimate density in the regions.
      \item Sum up to an estimate of the total.
    \end{itemize}
  \end{solution}

  \pause{}

  \begin{remark}
    \begin{itemize}
      \item Prone to errors, due to estimations.
      \item Universally verifiable, anyone with the photos can redo the 
        estimate.
      \item Eligibility verifiability if photos at one snapshot in time and no 
        overlap.
    \end{itemize}
  \end{remark}
\end{frame}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{solution}[CrowdSize app\footfullcite{CrowdSize}]
    \begin{itemize}
      \item User selects area on map.
      \item User selects an estimate for crowd density: light, medium or dense.
      \item App gives crowd size estimate based on size of the area and 
        density.
    \end{itemize}
  \end{solution}

  \pause{}

  \begin{remark}
    \begin{itemize}
      \item This is the same method as used by police.
      \item Not verifiable unless the user takes a picture of the crowd.
      \item Then it will be reduced to the previous method.
    \end{itemize}
  \end{remark}
\end{frame}
}

There is a body of work in the computer vision community, e.g.\ the work of 
\textcite{NNCrowdCounting}.
This class of methods requires photos or video surveillance of the protest 
location during the entire protest.
They generally include machine learning, and thus also require a training 
dataset to train the algorithms.
In the work by \textcite{NNCrowdCounting}, they actually train and evaluate 
their algorithm on different scenes, which might make this method easier to use 
for protesting.
We can provide universal verifiability (\cref{UniversalVerif}) with this 
method, since someone can always recount the participants using the recorded 
video material.
We might be able to provide some degree of individual verifiability 
(\cref{IndividualVerif}), but this might still be difficult.
Also, it is difficult (if not impossible) to not count people twice, thus we 
cannot argue for eligibility verifiability (\cref{EligibilityVerif}).
In theory, this class of methods will provide an upper bound, whereas our 
method provides a lower bound.
However, it is still difficult capture the entire location on surveillance 
video, which diminishes the argument for an upper bound.
The spatial and temporal verifiability properties are reduced to those of the 
video, which should be similar as in our discussion about the verifiability of 
photos above.

\mode<presentation>{%
\begin{frame}
  \begin{solution}[Computer vision]
    \begin{itemize}
      \item Record video of the event.
      \item Train algorithms on part of the data.
      \item Run algorithm to count the total.
    \end{itemize}
  \end{solution}

  \pause{}

  \begin{remark}
    \begin{itemize}
      \item Requires video-recording of the entire event.
      \item Difficult to record every part.
      \item Difficult (impossible?) to not record someone twice.
      \item Is verifiable, though limited, if the video is public.
      \item Authenticity can be questioned as with the photos.
    \end{itemize}
  \end{remark}
\end{frame}
}

@@

\mode<presentation>{%
\subsection{Signal-based methods}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{solution}[Wi-Fi tracking]
    \begin{itemize}
      \item Record unique Wi-Fi MAC addresses from people's smartphones.
    \end{itemize}
  \end{solution}

  \pause{}

  \begin{remark}
    \begin{itemize}
      \item Imprecise, requires assumptions.
      \item Half of smartphone users turn Wi-Fi off.
      \item MAC address randomization.
      \item Cannot verify.
    \end{itemize}
  \end{remark}
\end{frame}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{solution}[IMSI catchers]
    \begin{itemize}
      \item Use IMSI catchers to register unique phones.
      \item (Or use the network cell towers.)
    \end{itemize}
  \end{solution}

  \pause{}

  \begin{remark}
    \begin{itemize}
      \item Will include bystanders into the count.
      \item Privacy-invading due to phones being uniquely identifying.
      \item Cannot verify.
    \end{itemize}
  \end{remark}
\end{frame}
}

\Textcite{WifiCrowdCounting} also relies of Wi-Fi, but they instead use the 
Wi-Fi signal as a sonar to detect people.
However this method is designed for indoor use and does not scale to more than 
a crowd of 20 people.
In either case, this type of data cannot provide verifiability.

@@

%\mode<presentation>{%
%\subsection{Crowd sensing}
%}
%
%\dots

\mode<presentation>{%
\subsection{More exact methods}
}

The most closely related work is \textcite{CrowdCount}.
This is a web service which lets Alice create an event and Bob can submit his 
location to register that he is in Alice's event.
This solves the problem that it counts everyone (who submitted), not just the 
count at the snapshot of the photos.
However, there is no verification, i.e.\ the service must be trusted to behave 
honestly, but even then, nothing prevents Bob from submitting twice (violating 
eligibility verification, \cref{EligibilityVerif}).
Another downside is that the service also requires an Internet connection 
during the event to register as a participant.
This can make it difficult to use if e.g.\ Alice has organized a protest 
against the government, who shuts down the cellular network or Internet 
backbone as a means to censor the protest.

\mode<presentation>{%
\begin{frame}
  \begin{solution}[CrowdCount\footfullcite{CrowdCount}]
    \begin{itemize}
      \item Register an upcoming event.
      \item Let people \enquote{check-in} by submitting their location.
    \end{itemize}
  \end{solution}

  \pause{}

  \begin{remark}
    \begin{itemize}
      \item No verification, the service must be trusted.
      \item Nothing prevents Bob from checking in twice.
      \item Requires an Internet connection during the event.
    \end{itemize}
  \end{remark}
\end{frame}
}

>>>>

\section{Related work}%
\label{RelatedWork}

@@

@@

There is a body of work in the computer vision community, e.g.\ the work of 
\citet{NNCrowdCounting}.
This class of methods requires photos or video surveillance of the protest 
location during the entire protest.
They generally include machine learning, and thus also require a training 
dataset to train the algorithms.
In the work by \citet{NNCrowdCounting}, they actually train and evaluate their 
algorithm on different scenes, which might make this method easier to use for 
protesting.
We can provide universal verifiability (\cref{UniversalVerif}) with this 
method, since someone can always recount the participants using the recorded 
video material.
We might be able to provide some degree of individual verifiability 
(\cref{IndividualVerif}), but this might still be difficult.
Also, it is difficult (if not impossible) to not count people twice, thus we 
cannot argue for eligibility verifiability (\cref{EligibilityVerif}).
In theory, this class of methods will provide an upper bound, whereas our 
method provides a lower bound.
However, it is still difficult capture the entire location on surveillance 
video, which diminishes the argument for an upper bound.
The spatial and temporal verifiability properties are reduced to those of the 
video, which should be similar as in our discussion about the verifiability of 
photos above.

@@

@@

@@

\Citet{WifiCrowdCounting} also relies of Wi-Fi, but they instead use the Wi-Fi 
signal as a sonar to detect people.
However this method is designed for indoor use and does not scale to more than 
a crowd of 20 people.
In either case, this type of data cannot provide verifiability.

@@

The most closely related work is \citet{CrowdCount}.
This is a web service which lets Alice create an event and Bob can submit his 
location to register that he is in Alice's event.
This solves the problem that it counts everyone (who submitted), not just the 
count at the snapshot of the photos.
However, there is no verification, i.e.\ the service must be trusted to behave 
honestly, but even then, nothing prevents Bob from submitting twice (violating 
eligibility verification, \cref{EligibilityVerif}).
Another downside is that the service also requires an Internet connection 
during the event to register as a participant.
This can make it difficult to use if e.g.\ Alice has organized a protest 
against the government, who shuts down the cellular network or Internet 
backbone as a means to censor the protest.

### 2018-02-01 paper/SystemModel.tex
Removes beamerarticle and changes citations to natbib syntax

\mode*

@@

\mode<presentation>{%
\begin{frame}
  \begin{example}[Seoul 2016]
    \begin{itemize}
      \item Rallies every weekend.
      \item Starting midday, lasting to late night.
      \item Some stayed for several hours, some for only minutes.
    \end{itemize}
  \end{example}

  \pause{}

  \begin{example}[US 2017]
    \begin{itemize}
      \item Women's Marches in several locations.
      \item Marched some distance.
      \item One-time occurrence.
    \end{itemize}
  \end{example}
\end{frame}
}

\mode<presentation>{%
\begin{frame}
  \begin{example}[Venezuela 2017]
    \begin{itemize}
      \item Daily anti-government rallies.
      \item Multiple locations.
      \item Pro-government rallies too.
    \end{itemize}
  \end{example}
\end{frame}
}

@@

\begin{frame}
\begin{definition}[Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((cid, t, l)\) where
  \(cid\in \Z_{2^\lambda}\) is the cause\footnote{%
    I.e.\ the cause of the protest.
  } identifier,
  \(t = \interval{t_s}{t_e}\subseteq \R\) is a time interval and
  \(l = N_\epsilon(x, y)\subseteq \R^2\) is the location (an 
  \(\epsilon\)-neighbourhood of \((x,y)\)).
  A \emph{protest} is a set of subprotests sharing the same \(id\).
\end{definition}
\end{frame}

@@

\begin{frame}
\begin{definition}[Participation-proof share]
  A \emph{participation-proof share} \(w = (pid, cid, t, l, wid)\) is a tuple 
  where
  \(cid, t, l\) are as in \cref{DefProtest},
  \(pid\) is unique for a protester and \(cid\) pair, and
  \(wid\) is unique for a witness--protester pair.
  We let \(W\) be the set of all proof shares.
\end{definition}
\end{frame}

@@

\begin{frame}
\begin{definition}[Participation proof]
  A \emph{participation proof} of protester \(i\) participating in protest \(j\) 
  is the set
  \begin{align}
    \nonumber
    p_{i, j} =
    \left\{ (pid, cid, t, l, wid)\in W \mid
    %\right. &
    pid = i, cid = j,
    %\\ & \left.
    t \subseteq t_j, l\subseteq l_j \right\},
  \end{align}
  of all proof shares with the same protester and protest identifiers, witness 
  time interval \(t\) and location \(l\) is within those of the protest \(j\) 
  (i.e.\ \(t_j\) and \(l_j\)).
\end{definition}
\end{frame}

We can now define the participation count as follows.
\begin{frame}
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(cid\) as the 
  cardinality \(|P_{cid}^{s,\theta}|\) of the set of participation proofs \[
    P_{cid}^{s,\theta} = \left\{ p_{i,j} \mid
      j = cid, s(p_{i,j})\geq \theta \right\}
  \] for some strength function \(s\colon \powerset(W)\to \R_+\) and a threshold 
  \(\theta\).
\end{definition}

\pause{}

\mode<presentation>{%
  \begin{example}
    \begin{itemize}
      \item The strength function can regulate trust in witnesses.
      \item E.g.\ return the number of witnesses.
      \item \(\theta\) would control threshold of number of witnesses.
    \end{itemize}
  \end{example}
}
\end{frame}

The strength function \(s\) can be used to e.g.\ regulate trust in 
witnesses.
A trivial example would be for \(s\) to return the number of proof shares (i.e.\ 
witnesses) and thus let \(\theta\) to be the threshold of the number of required 
witnesses.

>>>>

@@

@@

\begin{definition}[Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((cid, t, l)\) where
  \(cid\in \Z_{2^\lambda}\) is the cause\footnote{%
    I.e.\ the cause of the protest.
  } identifier,
  \(t = \interval{t_s}{t_e}\subseteq \R\) is a time interval and
  \(l = N_\epsilon(x, y)\subseteq \R^2\) is the location (an 
  \(\epsilon\)-neighbourhood of \((x,y)\)).
  A \emph{protest} is a set of subprotests sharing the same \(id\).
\end{definition}

@@

\begin{definition}[Participation-proof share]
  A \emph{participation-proof share} \(w = (pid, cid, t, l, wid)\) is a tuple 
  where
  \(cid, t, l\) are as in \cref{DefProtest},
  \(pid\) is unique for a protester and \(cid\) pair, and
  \(wid\) is unique for a witness--protester pair.
  We let \(W\) be the set of all proof shares.
\end{definition}

@@

\begin{definition}[Participation proof]
  A \emph{participation proof} of protester \(i\) participating in protest \(j\) 
  is the set
  \begin{align}
    \nonumber
    p_{i, j} =
    \left\{ (pid, cid, t, l, wid)\in W \mid
    %\right. &
    pid = i, cid = j,
    %\\ & \left.
    t \subseteq t_j, l\subseteq l_j \right\},
  \end{align}
  of all proof shares with the same protester and protest identifiers, witness 
  time interval \(t\) and location \(l\) is within those of the protest \(j\) 
  (i.e.\ \(t_j\) and \(l_j\)).
\end{definition}

We can now define the participation count as follows.
\begin{definition}[Participation count]
  We define the \emph{participation count} of a protest \(cid\) as the 
  cardinality \(|P_{cid}^{s,\theta}|\) of the set of participation proofs \[
    P_{cid}^{s,\theta} = \left\{ p_{i,j} \mid
      j = cid, s(p_{i,j})\geq \theta \right\}
  \] for some strength function \(s\colon \powerset(W)\to \R_+\) and a threshold 
  \(\theta\).
\end{definition}
The strength function \(s\) can be used to e.g.\ regulate trust in witnesses.
A trivial example would be for \(s\) to return the number of proof shares (i.e.\ 
witnesses) and thus let \(\theta\) to be the threshold of the number of required 
witnesses.

### 2018-02-01 paper/intro.tex
Removes beamerarticle and changes citations to natbib syntax

\mode<presentation>{%
\subsection{What's the problem?}
}

\begin{frame}<presentation>
  \begin{block}{The crowd-counting problem}
    \begin{itemize}
      \item Alice organizes a protest against Eve's regime.
      \item Bob, Carol and others show up.
      \item We want to know how many showed up to support Alice.
    \end{itemize}
  \end{block}
\end{frame}

\mode<presentation>{%
\subsection{Why is it a problem?}
}

\mode<presentation>{%
\begin{frame}
  \begin{figure}
    \includegraphics[height=0.9\textheight]{Jacobs-method.jpg}
  \end{figure}
\end{frame}

\begin{frame}
  \begin{example}
    \begin{itemize}
      \item Computer vision does object recognition.
      \item Requires photos/video that cover the entire location, all the time.
      \item This will count people twice.
    \end{itemize}
  \end{example}

  \pause{}

  \begin{example}
    \begin{itemize}
      \item Scan active mobile phones in the area.
      \item This requires some extra equipment.
      \item This catches bystanders who are not protesting.
    \end{itemize}
  \end{example}
\end{frame}
}

\mode<none>{%
\begin{frame}
  \begin{example}
    \begin{itemize}
      \item South Korea 2016~\cite{2016DemonstrationsInSeoul}:
        approximate count by imagery.
        \begin{description}
          \item[Organizers] 1\,000\,000
          \item[Police] 260\,000
        \end{description}

        \pause{}

      \item US 2017~\cite{2017WomensMarchesInUS}:
        sum up people's approximations.
      \item This makes it even difficult to estimate the error.
    \end{itemize}
  \end{example}
\end{frame}
}

@@

\begin{frame}<presentation>
  \begin{block}{Verifying protest participation}
    \begin{itemize}
      \item Alice organizes a protest against Eve's regime.
      \item Bob, Carol and others show up.

        \pause{}

      \item {\color{green} Alice wants to show that many support her cause.}

        \pause{}

      \item {\color{red} Eve wants to show that few support Alice's cause.}
      \item It's an adversarial setting!
      \item We need verifiable results.
    \end{itemize}
  \end{block}
\end{frame}

@@

Voting has three requirements for 
verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{frame}
\begin{description}
  \item[Eligibility] anyone can verify that each vote cast is legitimate.
  \item[Universal verifiability] anyone can verify that the result is according 
    to the cast votes.
  \item[Individual verifiability] every voter can verify that their vote is 
    included in the result.
\end{description}
\end{frame}
We translate the votes into \emph{proofs of participation}.
Universal and individual verifiability remain the same: anyone can verify the 
participation count by counting the proofs.
The eligibility requirement is slightly different:
for protests the eligibility requirement must include temporal and spatial 
eligibility, i.e.\ that each proof of participation satisfies some temporal and 
spatial relation to the protest.
In essence, the proof must bind the person to the time and location of the 
protest.
We will define these more formally in \cref{Verifiability}.

\mode<presentation>{%
\begin{frame}
  \begin{description}
    \item[Privacy] no increased risk to participants.
  \end{description}
\end{frame}
}

@@

\mode<article>{%
\subsection{Contributions}
}

>>>>

@@

@@

Voting has three requirements for 
verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{description}
  \item[Eligibility] anyone can verify that each vote cast is legitimate.
  \item[Universal verifiability] anyone can verify that the result is according 
    to the cast votes.
  \item[Individual verifiability] every voter can verify that their vote is 
    included in the result.
\end{description}
We translate the votes into \emph{proofs of participation}.
Universal and individual verifiability remain the same: anyone can verify the 
participation count by counting the proofs.
The eligibility requirement is slightly different:
for protests the eligibility requirement must include temporal and spatial 
eligibility, i.e.\ that each proof of participation satisfies some temporal and 
spatial relation to the protest.
In essence, the proof must bind the person to the time and location of the 
protest.
We will define these more formally in \cref{Verifiability}.

@@

\subsection{Contributions}

### 2018-02-01 paper/properties.tex
Removes beamerarticle and changes citations to natbib syntax

\mode*
\section{Desired security properties}%
\label{Properties}

@@

\mode<presentation>{%
\begin{frame}
  \begin{block}{Alice the activist}
    \begin{itemize}
      \item Alice organizes the protest against Eve's regime.
      \item Alice wants to have a high participation count.
      \item She tries to increase it.
      \item So does \emph{all the protesters}.
    \end{itemize}
  \end{block}

  \pause{}

  \begin{block}{Eve the fake-news populist}
    \begin{itemize}
      \item Eve's regime is target of the protest.
      \item She wants to have a low participation count.
      \item She tries to decrease it.
    \end{itemize}
  \end{block}
\end{frame}
}

\mode<presentation>{%
\begin{frame}
  \begin{block}{Eve the totalitarian dictator}
    \begin{itemize}
      \item Eve wants to \enquote{convince} activists to support her.
      \item She wants to find all activists.
      \item She tries to identify (deanonymize) participants.
    \end{itemize}
  \end{block}
\end{frame}
}

\mode<presentation>{%
\begin{frame}
  \begin{block}{Rusuk the nation state}
    \begin{itemize}
      \item Rusuk benefits from the situation in Evestan.
      \item He wants the outcome to be the most beneficial.
      \item He will try to increase or decrease the participation count.
    \end{itemize}
  \end{block}
\end{frame}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{requirements}[V\ref*{EligibilityVerif}.]
  \item\label{CreatedAfterStart} Prove that the data was created after the 
    start of the event.
  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
    of the event.
  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
    physical location of the event.
  \item\label{CountOnce} Prove that no individual can be counted more than 
    once.
  \item\label{DesignatedEvent} Prove that the data is designated for the event.
\end{requirements}
\end{frame}
}

@@

There are two aspects of temporal eligibility.
The adversary can try to forge a witness for a future protest and the adversary 
can try to forge a witness for a past protest.

The first thing we want to do is to prevent Alice from collecting witnesses for 
a future protest.
For this, we introduce something we call a \emph{time-authenticator tag}.
This is an unpredictable value \(\tau_t\) which is published at time \(t\).
The idea is that it is difficult to guess \(\tau_t\) for a given \(t\) in 
advance, i.e.\ any use of \(\tau_t\) must have happened after time \(t\) with 
high probability.

\begin{definition}[Predicting the future]
  Let \(T_t = (\tau_i)_{i=0}^{t}\) be the sequence of time-authenticator tags up 
  until time \(t\), where \(\tau_i\in \Z_{2^\lambda}\) for all \(i\).
  (\(\lambda\) is the security parameter.)
  Let \A be \iac{PPT} adversary.
  The challenger gives \(T_{t-1}\) to \A.
  \A is allowed to query an oracle \(O\) which returns whether a guess is 
  correct or not.
  If \(\A^O(T_{t-1},1^\lambda)\) outputs \(\tau\) such that \(\tau = \tau_t\) 
  the adversary wins.
\end{definition}

We can see that if \(\tau_t\) is chosen uniformly randomly then the adversary's 
chance of winning will be
\begin{equation}
  \label{SuccessOfPrediction}
  \Prob{%
    \A^O(T_{t-1}, \lambda) = \tau_t
  } = \frac{p(\lambda)}{2^\lambda}
\end{equation}
for some polynomial \(p(\cdot)\).
This will be negligible for sufficiently a large \(\lambda\).

\begin{definition}[Collision]
  Given tag \(\tau\), probability of collision?
\end{definition}

\begin{definition}[Changing the past]
  Given a witness for time \(t\), change it to time \(t'\).
  \dots
\end{definition}

\begin{definition}[Forging past witnesses]
  \dots
\end{definition}

\begin{frame}
\begin{definition}[Forging temporal eligibility]
  \dots
\end{definition}
\end{frame}

@@

\begin{frame}
\begin{definition}[Forging spatial eligibility]
  \dots
\end{definition}
\end{frame}

@@

In voting, we have the following requirements:
\begin{frame}
\begin{requirements}[P]
\item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
  individual vote.
\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
  provide any data that can be used as a proof of how the voter voted.
\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
  with a coercer to prove the vote was cast in any particular way.
\end{requirements}
\pause{}
\mode<presentation>{%
  \begin{remark}
    P\ref{CoercionResistance} \(\implies\)
    P\ref{ReceiptFreeness} \(\implies\)
    P\ref{VotePrivacy}
  \end{remark}
}
\end{frame}
\Textcite{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
\cref{VotePrivacy}.
\Cref{CoercionResistance} is probably not possible to achieve for protests:
e.g.\ Eve can simply physically bring Alice to a protest against her will.
This leaves us with \cref{ReceiptFreeness,VotePrivacy}.

\mode<none>{%
\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item Coercion resistance is difficult to achieve for voting.
      \item It doesn't make much sense for protests.
      \item E.g.\ Eve physically brings Alice to a protest she doesn't want to 
        participate in.
      \item That leaves us with receipt freeness and vote privacy.
    \end{itemize}
  \end{remark}
\end{frame}
}

@@

\begin{frame}
\begin{definition}[Proof indistinguishability]
  \dots
\end{definition}
\end{frame}

@@

\begin{frame}
\begin{definition}[Receipt freeness/deniability]
  \dots
\end{definition}
\end{frame}

>>>>

\section{Desired security properties}%
\label{Properties}

@@

@@

@@

\begin{definition}[Forging temporal eligibility]
  \dots
\end{definition}

@@

\begin{definition}[Forging spatial eligibility]
  \dots
\end{definition}

@@

In voting, we have the following requirements:
\begin{requirements}[P]
\item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
  individual vote.
\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
  provide any data that can be used as a proof of how the voter voted.
\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
  with a coercer to prove the vote was cast in any particular way.
\end{requirements}
\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
\cref{VotePrivacy}.
\Cref{CoercionResistance} is probably not possible to achieve for protests:
e.g.\ Eve can simply physically bring Alice to a protest against her will.
This leaves us with \cref{ReceiptFreeness,VotePrivacy}.

@@

\begin{definition}[Proof indistinguishability]
  \dots
\end{definition}

@@

\begin{definition}[Receipt freeness/deniability]
  \dots
\end{definition}

### 2018-02-01 paper/protocol.tex
Removes beamerarticle and changes citations to natbib syntax

\mode*
\section{Protocol}

@@

\begin{frame}
\begin{figure}
  \centering
  \includegraphics{proofshare.tikz}
%  \begin{tikzpicture}[%
%    -Latex,
%    item/.style={rectangle,draw},
%    edge from parent/.style={}
%    ]
%    \tikzset{%
%      %grow'=left,%
%      %level distance=5em%
%    }
%    \node[item] (proof) {Proof share}
%      child {%
%        node[item] (pid) {$pid$}
%        child {%
%          node[item] (cid) {$cid$}
%          child {%
%            node[item] (manifesto) {Manifesto}
%          }
%        }
%      }
%      child {%
%        node[item] (wid) {$wid$}
%      }
%      child {%
%        node[item] (ts) {$t_s$}
%      }
%      child {%
%        node[item] (l) {$l$}
%      }
%      child {%
%        node[item] (wsig) {$wsig$}
%      }
%      ;
%
%      \path[every node/.style={font=\small}]
%      (pid) edge node [anchor=south east] {$\in$} (proof)
%      (wid) edge node [anchor=east] {$\in$} (proof)
%      (ts) edge node [anchor=east] {$\in$} (proof)
%      (l) edge node [anchor=west] {$\in$} (proof)
%      (wsig) edge node [anchor=south west] {$\in$} (proof)
%      ;
%
%      \path[every node/.style={font=\small}]
%      (manifesto) edge node [anchor=east] {$H(\cdot)$} (cid)
%      (cid) edge node [anchor=east] {$PRF_{k_P}(\cdot)$} (pid)
%      (pid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot)$} (wid)
%      % wsig
%      (l) edge[bend right] (wsig)
%      (ts) edge[bend right] (wsig)
%      (wid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot, \cdot, 
%        \cdot)$} (wsig)
%      ;
%
%  \end{tikzpicture}
  \mode<article>{%
  \caption{%
    Structure of a proof share.
    The protester \(P\)'s identifier \(pid\) is computed using the protester's 
    key \(k_P\).
    The witness \(W\)'s identifier \(wid\) is computed using the witness's key 
    \(k_W\).
    \(t_s\) is a time interval and \(l\) is the coordinates of an area.
    The protest (cause) identifier \(cid\) is the hash value of the manifesto.
  }}%
  \label{fig:ProofFig}
\end{figure}%
\end{frame}

\begin{frame}
\begin{figure}
  \centering
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & cid\gets H(\text{manifesto}), \\
        & pid\gets PRF_{k_P}(cid) \\
      P\to W\colon & pid \\
      W\leftrightarrow P\colon & \text{perform distance bounding} \\
      W\colon & wid\gets PRF_{k_W}(pid), \\
        & wsig\gets PRF_{k_W}(wid, t_s, l) \\
      W\to P\colon & (wid, t_s, l, wsig) \\
      W\to S\colon & H(pid, wid, t_s, l, wsig) \\
      P\to S\colon & H(pid, wid, t_s, l, wsig) \\
      W\to S\colon & (pid, wid, t_s, l, wsig),\\
        & NIZK(wid = PRF_{k_W}(pid), wsig = PRF_{k_W}(wid, t_s, l), \exists 
        sign(k_W)) \\
      P\to S\colon & (pid, wid, t_s, l, wsig),\\
        & NIZK(pid = PRF_{k_P}(cid), \exists sign(k_P))
    \end{align*}
  \end{minipage}
  \mode<article>{%
  \caption{%
    An overview of message exchanges.
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }}%
  \label{fig:ProtocolOverview}
\end{figure}
\end{frame}

@@

Next we need to consider the protesters' identifiers to prevent Sybil attacks.
\Textcite{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another scheme that makes it non-interactive, e.g.\ by 
  \Textcite{Psignatures}, see issue \#27.
}, where \(n = 1\) in our scenario.
Alice has a \ac{PRF} key \(k\) and a blind signature on \(k\) included in her 
national identity-card (by assumption).
She will use \(k\) to compute \(pid\gets PRF_k(cid)\), which is her anonymous 
identity during the protest (shown as \(pid\) in \cref{fig:ProofFig}).

>>>>

\section{Protocol}

@@

\begin{figure}
  \centering
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protester \(P\)'s identifier \(pid\) is computed using the protester's 
    key \(k_P\).
    The witness \(W\)'s identifier \(wid\) is computed using the witness's key 
    \(k_W\).
    \(t_s\) is a time interval and \(l\) is the coordinates of an area.
    The protest (cause) identifier \(cid\) is the hash value of the manifesto.
  }%
  \label{fig:ProofFig}
\end{figure}%

\begin{figure}
  \centering
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & cid\gets H(\text{manifesto}), \\
        & pid\gets PRF_{k_P}(cid) \\
      P\to W\colon & pid \\
      W\leftrightarrow P\colon & \text{perform distance bounding} \\
      W\colon & wid\gets PRF_{k_W}(pid), \\
        & wsig\gets PRF_{k_W}(wid, t_s, l) \\
      W\to P\colon & (wid, t_s, l, wsig) \\
      W\to S\colon & H(pid, wid, t_s, l, wsig) \\
      P\to S\colon & H(pid, wid, t_s, l, wsig) \\
      W\to S\colon & (pid, wid, t_s, l, wsig),\\
        & NIZK(wid = PRF_{k_W}(pid),\\
        & wsig = PRF_{k_W}(wid, t_s, l),\\
        & \exists sign(k_W)) \\
      P\to S\colon & (pid, wid, t_s, l, wsig),\\
        & NIZK(pid = PRF_{k_P}(cid), \exists sign(k_P))
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of message exchanges.
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}

@@

Next we need to consider the protesters' identifiers to prevent Sybil attacks.
\Citet{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another scheme that makes it non-interactive, e.g.\ by 
  \citet{Psignatures}, see issue \#27.
}, where \(n = 1\) in our scenario.
Alice has a \ac{PRF} key \(k\) and a blind signature on \(k\) included in her 
national identity-card (by assumption).
She will use \(k\) to compute \(pid\gets PRF_k(cid)\), which is her anonymous 
identity during the protest (shown as \(pid\) in \cref{fig:ProofFig}).
